Ultrafast Electron Microscopes: Design Criteria, Electron Sources, and Column Modeling

### 2013-04-08 inc/photocathode/single_photon/single_photon.tex
clean-up binning problem for single_photon plot
more tweaks to single_photon

\begin{figure}
  \centering
  \input{w_plot}
  \caption[Single-photon photoemission from Tungsten]{
    Single-photon photoemission from Tungsten.
    Circles indicate relative electron yield (per pulse), the linear fit line indicates a single-photon process.
    The Fourier plane spot size (squares), related to the initial transverse momentum variance, does not depend on laser pulse energy, as expected.
  }
  \label{fig:single_photon_tungsten}
\end{figure}

>>>>

\begin{figure}
  \centering
  \input{w_plot}
  \caption[Single-photon photoemission from Tungsten]{
    Single-photon photoemission from Tungsten.
    The good linear fit (green) to the relative electron yield (squares) indicates a single-photon process.
    The Fourier plane spot size (squares), related to the initial transverse momentum variance, do not depend on laser pulse energy, as expected.
  }
  \label{fig:single_photon_tungsten}
\end{figure}
